---
title: "NYCDSA R Project Notebook - Luigi Balarinni 2022/12/16"
output: html_notebook
---

```{r}
# install.packages("shiny")
# install.packages("rjson")
# install.packages("Rtools")
library(dplyr)
library(jsonlite)
library(tidyverse)
library(ggplot2)
library(jsonlite)
library(shiny)
library(here)

setwd(here())
result <- jsonlite::fromJSON(txt = "./Bronx.json", flatten = TRUE)
json_bronx <- as.data.frame(result)
df_bronx <- data.frame(sapply(json_bronx,c))

result <- jsonlite::fromJSON(txt = "./Brooklyn.json")
json_bk <- as.data.frame(result)
df_bk <- data.frame(sapply(json_bk,c))

result <- jsonlite::fromJSON(txt = "./Manhattan.json")
json_manh <- as.data.frame(result)
df_manh <- data.frame(sapply(json_manh,c))

result <- jsonlite::fromJSON(txt = "./Queens.json")
json_queens <- as.data.frame(result)
df_queens <- data.frame(sapply(json_queens,c))

result <- jsonlite::fromJSON(txt = "./Staten Island.json")
json_st <- as.data.frame(result)
df_st <- data.frame(sapply(json_st,c))

```

Now that all 5 boroughs have been put into dataframes. Let's make a 6th one of them all.

```{r}
df_all = data.frame(sapply(rbind(df_bronx, df_bk, df_manh, df_queens, df_st),c))
df_all
```

Plotting Inspection Scores for All and each Borough.

```{r}
p = ggplot(df_all, aes(x=Grade)) + geom_bar() + ggtitle("All 5 Boros")
p <- p + theme(axis.text = element_text(size = 12)) + theme(axis.title = element_text(size = 12))
p
ggsave("./grade_all.png", p, width=8, height=4)

p = ggplot(df_bronx, aes(x=Grade)) + geom_bar() + ggtitle("Bronx")
p <- p + theme(axis.text = element_text(size = 12)) + theme(axis.title = element_text(size = 12))
p
ggsave("./grade_bronx.png", p, width=8, height=4)

p = ggplot(df_bk, aes(x=Grade)) + geom_bar() + ggtitle("Brooklyn")
p <- p + theme(axis.text = element_text(size = 12)) + theme(axis.title = element_text(size = 12))
p
ggsave("./grade_bk.png", p, width=8, height=4)

p = ggplot(df_manh, aes(x=Grade)) + geom_bar() + ggtitle("Manhattan")
p <- p + theme(axis.text = element_text(size = 12)) + theme(axis.title = element_text(size = 12))
p
ggsave("./grade_MH.png", p, width=8, height=4)

p = ggplot(df_queens, aes(x=Grade)) + geom_bar() + ggtitle("Queens")
p <- p + theme(axis.text = element_text(size = 12)) + theme(axis.title = element_text(size = 12))
p
ggsave("./grade_queens.png", p, width=8, height=4)

p = ggplot(df_st, aes(x=Grade)) + geom_bar() + ggtitle("Staten Island")
p <- p + theme(axis.text = element_text(size = 12)) + theme(axis.title = element_text(size = 12))
p
ggsave("./grade_st.png", p, width=8, height=4)
```

Inspection results As of December 13th, 2022
Note: The Restaurant inspection reports identify restaurants by their CAMIS and their violation details.

```{r}
result2 <- jsonlite::fromJSON(txt = "https://data.cityofnewyork.us/resource/43nn-pn8j.json")
json_insp <- as.data.frame(result2)
df_violations <- data.frame(sapply(json_insp,c))
names(df_violations) = toupper(names(df_violations))
df_violations <- df_violations[order(df_violations$CAMIS),] # Sort by CAMIS number, effectively, grouping them
rownames(df_violations) <- NULL # Reset the index

cols =  c("CAMIS", "Total", "Critical", "Not Critical", "Not Applicable")
df_violations_total = data.frame( matrix(nrow =0, ncol=length(cols)))
colnames(df_violations_total) = cols
print(colnames(df_violations_total))
  
# for (i in ids_uniq) {
#   ct_total = nrow(subset(df_violations, df_violations$CAMIS == i))
#   ct_cr = nrow(subset(df_violations, df_violations$CAMIS == i & df_violations$CRITICAL.FLAG == "Critical"))
#   ct_nc = nrow(subset(df_violations, df_violations$CAMIS == i & df_violations$CRITICAL.FLAG == "Not Critical"))
#   ct_na = nrow(subset(df_violations, df_violations$CAMIS == i & df_violations$CRITICAL.FLAG == "Not Applicable"))
#   new_row = c(i, ct_total, ct_cr, ct_nc, ct_na)
#   df_violations_total = rbind(df_violations_total, new_row)
#   # print(paste("CAMIS ID:", i, "has total violations of:", ct_total, "of which Critical/NC/NA are", ct_cr, ct_nc, ct_na))
# }
# colnames(df_violations_total) = cols
# # write.csv(df_violations_total, "./df_violations_total.csv", row.names=FALSE)
# df_violations_total = data.frame(read_csv(df_violations_total, "df_violations_total.csv", row.names=FALSE))
df_violations_total$Total = as.integer(df_violations_total$Total)
df_violations_total$Critical = as.integer(df_violations_total$Critical)
df_violations_total$`Not Critical` = as.integer(df_violations_total$`Not Critical`)
df_violations_total$`Not Applicable` = as.integer(df_violations_total$`Not Applicable`)
head(df_violations_total)
df_violations_total3 = as.data.frame(read_csv("df_violations_total.csv"))
head(df_violations_total3)
# df_all %>% filter(MostRecentVendingBoro == "Bronx") %>% group_by(Cuisine) %>% summarise()
```



Plotting the Distribution of violation types
```{r}
p = ggplot() +
  geom_histogram(data = df_violations_total, aes(x=`Not Critical`), color="black", fill="orange", binwidth=1) +
  geom_histogram(data = df_violations_total, aes(x=Critical), color="black", fill="red", binwidth=1) +
  ggtitle("Critical (Red) vs Not (Orange)")
p <- p + theme(axis.text = element_text(size = 12)) + theme(axis.title = element_text(size = 12))
p
ggsave("./histo_violat_crit_notCrit.png", p, width=8, height=8)

p = ggplot() +
  geom_histogram(data = df_violations_total, aes(x=Total), color="black", fill="black", binwidth=2) +
  ggtitle("Total Number of Violations")
ggsave("./histo_violat_total.png", p, width=8, height=8)

p = ggplot() +
  geom_histogram(data = df_violations_total, aes(x=`Not Applicable`), color="black", fill="black", binwidth=1) +
  ggtitle("Not Applicable = Successful Inspection")
ggsave("./histo_violat_NA.png", p, width=8, height=8)
```

Let's see a bar chart of the number of Cuisine categories.

```{r}
p = ggplot(df_all, aes(x=Cuisine)) + geom_bar()
p = p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggsave("./histo_cusines.png", p, width=12, height=4)
```


```{r}
head(df_all)
ids_uniq = unique(df_violations$CAMIS)
ids_uniq2 = unique(df_)
nrow(subset(df_all, df_all$Grade == "Not Yet Graded"))
nrow(subset(df_all, df_all$Grade == "Grade Pending"))
nrow(subset(df_all, df_all$Grade == "Closed"))
```

```{r}
df_violations_total[order(-df_violations_total$Critical),] # Sort by CAMIS number, effectively, grouping them
rownames(df_violations) <- NULL # Reset the index
df_violations
# worst_perf = subset(df_violations_total, df_violations_total$Critical >0)
worst_perf = df_violations_total[order(-df_violations_total$Critical),]
rownames(worst_perf) <- NULL
worst_perf
list_worst = worst_perf[worst_perf$CAMIS[1:20],]
list_worst

df_worst = df_all[df_all$CurrentDecalNumber %in% worst_perf$CAMIS[1:20],c('EntityName','MostRecentVendingLocation', 'MostRecentVendingBoro')]
rownames(df_worst) <- NULL
df_worst
```

